Insurance choice, decision assistance, and insurer steering

### 2021-03-29 finals/lunch-and-learn/lunch-learn-202103.Rmd
update slides

.center[
<iframe width="800" height="500" src="https://www.youtube.com/embed/oWXNf3JVWpI?start=146&end=271" frameborder="0" allowfullscreen></iframe>
]

>>>>

.center[
<iframe width="800" height="500" src="https://www.youtube.com/embed/oWXNf3JVWpI?start=146&end=272" frameborder="0" allowfullscreen></iframe>
]
